---
title: "Coding_Exercise"
author: "Scott Otto"
date: "2025-10-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("setup.R")
```

```{r}
data("knz_bison")
```

# 1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation.

```{r}
knz_bison <- knz_bison %>%
  mutate(age_at_observation = rec_year - animal_yob)
```

# 2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

```{r}
bison_weight_filter <- function(data, weight_threshold) {
  knz_bison %>%
    filter(animal_weight >= weight_threshold)
}


bison_weight_filter(knz_bison, 500) %>%
  View()
```

# 3. Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}
knz_bison %>%
  ggplot(aes(x = animal_sex, y = animal_weight, fill = animal_sex)) +
  geom_boxplot() +
  labs(
    title = "Weight Distribution Between Male and Female Bison",
    x = "Sex",
    y = "Animal Weight (kg)"
  ) +
  theme_minimal()

t.test(animal_weight ~ animal_sex, data = knz_bison)
```


